# **Show any code that is needed to load the data**  
```{r}
setwd("~/School/Coursera")
rm(list = ls())
activity <- read.csv("activity.csv", colClasses = c("numeric", "character", "integer"))
```

# **Process the data into a format suitable for your analysis**  

```{r}
library(plyr)
library(dplyr)
library(lubridate)
library(ggplot2)

total_steps <- tapply(activity$steps, activity$date, FUN = sum, na.rm = TRUE)
activity$date <- ymd(activity$date)
```
# **Part One**  
### **What is the mean total number of steps taken per day?**  
```{r}
mean(total_steps)
median(total_steps)
```
### **Calculate the total number of steps taken per day**
```{r}
steps <- activity %>%
  filter(!is.na(steps)) %>%
  group_by(date) %>%
  summarize(steps = sum(steps)) %>%
  print
```
### **Make a histogram of the total number of steps taken each day**  
```{r}
ggplot(steps, aes(x = date, y = steps)) + geom_histogram(stat = "identity") + xlab("Dates") + ylab("Steps") + labs(title = "Total number of steps per day")
```

# **Part Two**
### **What is the average daily activity pattern?**  
```{r}
daily <- activity %>%
  filter(!is.na(steps)) %>%
  group_by(interval) %>%
  summarize(steps = mean(steps)) %>%
  print
```
### **Make a time series plot of the 5-minute interval and the average number of steps taken, averaged across all days**  
```{r}
plot(daily, type = "l")
```

### **Which 5-minute interval, on average across all the days in the dataset, contains the max number of steps?**  
```{r}
daily[which.max(daily$steps),]$interval
```
### **Imputing missing values**  
### Calculate and report the total number of missing values in the dataset  
```{r}
missing <- sum(is.na(activity))
missing
```  
### **Create a new dataset that is equal to the original dataset but with the missing data filled in**  
```{r}
filled <- activity %>%
  group_by(interval) %>%
  mutate(steps = ifelse(is.na(steps), mean(steps, na.rm = TRUE), steps))
summary(filled)
```
### **Make a histogram of the total number of steps taken each day**  
```{r}
new_steps <- filled %>%
  group_by(date) %>%
  summarize(steps = sum(steps)) %>%
  print
ggplot(new_steps, aes(x = date, y = steps)) + geom_histogram(stat = "identity") + xlab("Dates") + ylab("Imputed Steps") + labs(title = "Total Number of Steps per Day")
```  

### **Calculate and report the mean and median total number of steps taken per day**  
```{r}
imputed_steps <- tapply(filled$steps, filled$date, FUN = sum, na.rm = TRUE)
filled$date <- ymd(filled$date)
mean(imputed_steps)
median(imputed_steps)
```
### **Do these values differ from the estimates from the first part of the assignment?**  
```{r}
mean(total_steps) == mean(imputed_steps)
median(total_steps) == median(imputed_steps)
summary(total_steps)
summary(imputed_steps)
```
### **What is the impact of imputing missing data on the estimates of the total daily number of steps?**
```{r}
summary(imputed_steps) - summary(total_steps)
par(mfrow = c(2, 1))
hist(imputed_steps, col = "red")
hist(total_steps, col = "blue")
```

# **Part 3**  

### **Are there differences in activity patterns between weekdays and weekends?**
```{r}
dofw <- function(date) {
  if (weekdays(as.Date(date)) %in% c("Saturday", "Sunday")){
    "weekend"
  } else {
    "weekday"
  }
}
filled$daytype <- as.factor(sapply(filled$date, dofw))
```
### **Make a panel plot containing a time series plot of the 5-minute interval and the average number of steps taken, averaged across all weekday days or weekend days**  
```{r}
par(mfrow = c(2, 1))
for (type in c("weekend", "weekday")) {
  steps_type <- aggregate(steps ~ interval, data = filled, subset = filled$daytype == type, FUN = mean)
  plot(steps_type, type = "l", main = type)
}
```
